R Notebook

### 2022-02-16 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.16.22
graph's n stuff

    DataFrame:
  smugCovIdx
  network_nodes <- smugCovIdx << "dnkName"

@@

@@

            # list the names:  edge attributes
  network::list.edge.attributes(smugEL_sn)
      #   summarize: numeric network attribute
  summary(smug_sn%v%"dnkName")

@@

#   Week 2: Basic Network Structure: Smuggler's Cove Drink Index

@@

## Dyad Census
Classifies all dyads in the network as: - 
Reciprocal (mutual), 
or mut - Asymmetric (non-mutual), 
or asym, 
and - Absent, or null

@@

  igraph::dyad.census(smugEL_ig)

@@

## Local Transivity or Clustering
`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.

```{r iGraph:Local transitivity, echo=TRUE}

#     check ego network transitivity
transitivity(smugEL_ig,
             type="local", 
             vids=V(smugEL_ig)
             [c("Bischeri",
                "Castellani", 
                "Medici",
                "Ridolfi")]) 
#     get global clustering cofficient
  transitivity(smugEL_ig, type="global")

@@

@@

 # Is Ego an Isolate?
 is.isolate(smugEL_sn, ego, g=1, diag=FALSE)

 # Adds n isolates to the graph (or graphs)
 add.isolates(smugEL_sn, n, return.as.edgelist = FALSE)

@@

    # Number of components
 igraph::components(smugEL_ig)$no

@@

```{r Statnet, echo=TRUE}

# get network density: with possible loops
 network.density(smugEL_sn)

 # get network density without loops: statnet
 gden(smugEL_sn, diag=FALSE)

@@

```{r igraph: network density, echo=TRUE}
#get network density without loops: igraph
 network.density(smugEL_ig,loops=TRUE)

 # get network density
 network.density(smugEL_ig)
 # provides an incorrect density calculation as the default assumes that loops are not included but does not remove them

>>>>

    DataFrame:
  smugCovIdx
            colname: "dnkName" "dnkIng"  "ingType"
  network_nodes <- smugCovIdx << "dnkName"

@@

  Edge Vetex:
              dnkName
  Edge Attributes:
                  dnkIng
                  ingType

@@

            # list the names:  edge attributes
  network::list.edge.attributes(smugEL_sn)
      #   summarize: numeric network attribute
  summary(smugEL_sn%v%"dnkName")

@@

## igraph: Exploring Network

```{r}
library("igraph")

```
IGRAPH 574c3d4 UN-- 274 672 -- 
+ attr: name (v/c), 
        dnkName (v/c), 
        dnkIng (e/c),
      | ingType (e/c)
+ edges from 574c3d4 (vertex names):

#   Week 2: Basic Network Structure: Smuggler's Cove Drink Index
We can break large social networks down into their constituent parts. These constituent parts are referred to as “motifs”. The most basic motif consists of two nodes and is called a dyad. Edges in a network signify the presence or absence of dyadic relations. It follows that a dyad in an undirected network can have two unique configurations: connected or disconnected; and three unique configurations in a directed network (mutual, assymetric, and null)

@@

## Dyad Census

Classifies all dyads in the network as: - 
Reciprocal (mutual), 
or mut - Asymmetric (non-mutual), 
or asym, 
and - Absent, or null

@@

graph.density(smugEL_ig)
    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network

      # Generating a random graph for comparison
# ?erdos.renyi.game
      ## In an erdos.renyi.graph, each edge has the same probability of being created. We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.

smugEL_igNod <- vcount(smugEL_ig)

smugEL_igDen <- graph.density(smugEL_ig)

smugEL_igRandoG <- 
  erdos.renyi.game(
    n = smugEL_igNod, 
    p.or.m = smugEL_igDen, 
    directed = F) 
      # where n is the number of nodes, 
      # p.or.m is the probability of drawing an edge, 
      #directed is whether the network is directed or not

#**plot(smugEL_igRandoG, ...** in .R notebook  
     # vertex.size = 5, 
     # vertex.label = 1, 
     # edge.curved = .1, 
     # vertex.color = "tomato", 
     # edge.arrow.size = .1, 
     # edge.width = .5, 
     # edge.color = "grey60")

@@

## Local Transivity or Clustering
`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
```{r iGraph: Transitivity: Network}
#     get global clustering cofficient
  transitivity(smugEL_ig, type="global")

@@

```{r iGraph:Local transitivity: Node List & Ego Network, echo=TRUE}

#     check ego network transitivity
transitivity(smugEL_ig,
             type="local", 
             vids=V(smugEL_ig)
             [c("Bischeri",
                "Castellani", 
                "Medici",
                "Ridolfi")]) 
```

@@

 # Is Ego an Isolate?
 is.isolate(smugEL_sn, ego_exp, g=1, diag=FALSE)

 # Adds n isolates to the graph (or graphs)
 add.isolates(smugEL_sn, n_umber, return.as.edgelist = FALSE)

@@

    # Number of components
 igraph::components(smugEL_ig)$no 
      ##**NOTE:** $no prevents a list of comonents from being printed

@@

```{r Statnet: Network Density, echo=TRUE}

            # get network density: with possible loops
   network.density(smugEL_sn)
          ##**WARNING: Network is multiplex - no general way to define density.**

 # get network density **with** loops: statnet
 gden(smugEL_sn, diag=F)

@@

```{r igraph: network density, echo=TRUE}

    #get network density **with** loops
 network.density(smugEL_ig)
 class(smugEL_ig)
          ##**NOTE** provides an incorrect density calculation 
          ## as the default assumes that loops are not included but does not remove them
